---
title: "Homework 6"
author: "Riya Bhilegaonkar"
date: "2022-11-27"
output: github_document
---

```{r, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

### Problem 1


### Problem 2
Creating a `city_state` variable and a binary variable `resolved` to indicate whether a homicide is solved. Filtering for cities that do not include Dallas(TX), Phoenix(AZ), Kansas City(MO) and Tulsa(AL) and filtering for the victim race of white or black. The `victim_age` variable is changed to a numeric variable. 

```{r}
homicide_data = read_csv("data/homicide-data.csv") %>%
  janitor::clean_names() %>%
  mutate(city_state = str_c(city,    state, sep=", "), resolved = as.numeric(disposition == "Closed by arrest"))%>%
  filter(city_state !="Dallas, TX" | city_state !="Phoenix, AZ" | city_state!="Kansas City, MO" | city_state != "Tulsa, AL", victim_race == "White" | victim_race == "Black") %>%
  mutate(victim_age = as.numeric(victim_age), victim_race = fct_relevel(victim_race, "White"))%>%
  select(city_state, victim_sex, resolved, victim_age, victim_race)
View(homicide_data)

```

For the city of Baltimore, MD we use the `glm` function to fit a logistic regression with resolved vs unsolved as the outcome and victim age, sex and race as predictors, saving the results as an R object. 
```{r}
fit_logistic = homicide_data %>%
  filter(city_state == "Baltimore, MD")%>%
  glm(resolved ~ victim_age + victim_race + victim_sex, data =., family = binomial()) 
```

Displaying the estimate and the confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.
```{r}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>% # figure out CI calculations for OR??%>%
   filter(term=="victim_sexMale")%>%
  mutate(CI.low = OR - std.error*1.96, CI.high = OR + std.error*1.96)%>%
  select(term, log_OR = estimate, OR, CI.low, CI.high) %>% 
  knitr::kable(digits = 3)
```

Running a `glm` for each city in the dataset and extracting the adjusted odds ratio and CI for solving homicides comparing male victims to female victims. Creating a dataframe with estimated ORs and CIs for each city: 

```{r}
## fix this entirely
homicide_data %>%
  nest(data=-city_state)%>%
  mutate(
    models = map(data, ~glm(resolved ~ victim_race + victim_sex, data = homicide_data, family = binomial())),
    results = map(models, broom::tidy)) %>%
  select(-data, -models)%>%
  unnest(results)%>%
mutate(OR = exp(estimate)) %>% # figure out CI calculations for OR??
  mutate(CI.low = OR - std.error*1.96, CI.high = OR + std.error*1.96)%>%
  select(city_state, term, log_OR = estimate, OR, CI.low, CI.high) %>% 
  #filter(term=="victim_sexMale")%>%
  knitr::kable(digits = 3)
  
```




### Problem 3